### 2022-09-08 doc/src/CSRs.tex
Add a section speaking generally about virtual instruction exceptions

>>>>

%-----------------------------------------------------------------------
\section{Virtual instruction exceptions}

Following the default rules for the hypervisor extension, attempts
from \mbox{VS-mode} to directly access a hypervisor or VS CSR, or
from \mbox{VU-mode} to access any supervisor-level CSR (including
hypervisor and VS CSRs), usually raise not an illegal instruction
exception but instead a virtual instruction exception.
For details, see the {\RISCV} Privileged Architecture.
